---
title: MIS-C Project Update 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  beamer_presentation: 
    pandoc_args: ["+RTS", "-K64m","-RTS"]
    slide_level: 2
    toc: false
    df_print: kable
    includes:
      in_header: reportformat.tex
classoption: "aspectratio=169"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(knitr)
```

```{r}
# prs <- read_csv('../../data/processed/genome1000/prs/nohla/prs_df.csv')
```

# Background

- MIS-C cohort
    * 92 MIS-C positive and COVID positive
    * 14 MIS-C positive and COVID negative
    * 30 MIS-C negative and COVID positive

- HGI Canadian cohort
    * 777 samples
    
- 1000 Genome cohort
    * 2504 samples
    
- PRS generated from HGI summary statistics (hospitalized vs non-hospitalized)



# Preprocess

## Number of SNPs break down in each step
+------------+-----------+----------+-------------+------------+---------+----------+
|            | Filter by | MAF      | Exclude     | Exclude    | Merged  | After    |
|            | HGI SNPs  | >0.05    | mis-matches | HLA region |         | clumping |
+------------+-----------+----------+-------------+------------+---------+----------+
| MIS-C      | 5896386   | 4663790  | 4663786     | 4633346    |         |          |
+------------+-----------+----------+-------------+------------+---------+----------+
| HGICA      | 5630565   | 4318367  | 4318360     | 4289152    | 3921924 | 144086   |
+------------+-----------+----------+-------------+------------+---------+----------+
| Genome1000 | 4504999   | 4504999  | 4504989     | 4474762    |         |          |
+------------+-----------+----------+-------------+------------+---------+----------+


- HLA region - Chr6 position 25,000,000-35,000,000.

- Clumping parameters - $r^2$ 0.1, kb=500


## Number of SNPs by p-value threshold - Merged cohort


```{r}
clump <- read_table('../../data/processed/genomehgimisc136/clumped/nohla/clump.clumped',col_names = T)
breaks <- list.files('../../data/processed/genomehgimisc136/prs/nohla',pattern = '*.profile$',full.names = T) %>% 
  str_extract('(0\\.)?\\d+(?=.profile)') %>% 
  as.numeric() %>% 
  sort() %>% 
  c(0,.)
labels <- str_c('<',breaks[-1])
clump_s <- clump %>% 
  mutate(
    `P threshold` = cut(P,breaks = breaks, labels = labels)
  ) %>% 
  count(`P threshold`) %>% 
  mutate(
    n = cumsum(n)
  )
clump_s
```


# Preliminary results

## PRS distributions - Violin plot

```{r}
include_graphics('../../figures/prs/genomehgimisc136/nohla/prs_violin.pdf')
```


## PRS distributions - Histogram

```{r}
include_graphics('../../figures/prs/genomehgimisc136/nohla/prs_hist.pdf')
```

## Variation explained - MIS-C vs COVID+

```{r}
include_graphics('../../figures/prs/varexp.pdf')
```
